Manuscript draft

### 2019-06-19 manuscript/manuscript draft.Rmd
updated manuscript draft

Analyses were conducted on data contained in the open-access ForC database [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc:_2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from original publications and existing data compilations and databases. Associated data, such as stand age, measurement methodologies, and disturbance history, are also included. For each site, site geographic co-ordinates were used to extract the Koeppen-Geiger zone from the ESRI Koeppen-Geiger map [cite], and the FAO Global Ecological Zone from the ???. Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on old-growth forests in temperate and boreal regions. ForC currently contains [] records from [] plots, representing [] distinct geographic areas across all forested biogeographic and climate zones.

@@

*How do carbon fluxes vary with latitude?* All major carbon fluxes increase with decreasing latitude. All models were improved by the inclusion of altitude as a fixed effect, with carbon fluxes showing a significant decrease with increasing altitude.

*Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?* All major carbon fluxes show similar responses to climate variables. Of the climate variables tested, annual wet days, aridity, cloud cover, mean diurnal temperature range and precipitation seasonality were poor explainers of variation in primary productivity. 
Carbon fluxes show a linear increase with increasing mean annual temperature. However, they show a saturation point with mean annual precipitation, potential evapotranspiration, and vapour pressure deficit.
Generally, the climate variables which explain the highest amount of variation in carbon fluxes are temperature seasonality, mean annual temperature, annual temperature range, and vapour pressure. For measures of aboveground woody productivity (ANPP_woody and ANPP_woody_stem), vapour pressure deficit,  potential evapotranspiration, and mean annual temperature are the strongest predictors.

>>>>

Analyses were conducted on data contained in the open-access ForC database [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc:_2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from original publications and existing data compilations and databases. Associated data, such as stand age, measurement methodologies, and disturbance history, are also included. For each site, site geographic co-ordinates were used to extract the Koeppen-Geiger zone from the ESRI Koeppen-Geiger map [cite], and the FAO Global Ecological Zone from the ???. Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on old-growth forests in temperate and boreal regions. ForC currently contains 29768 records from 5227 plots, representing 20 distinct ecozones across all forested biogeographic and climate zones.

@@

*How do carbon fluxes vary with latitude?* All major carbon fluxes increase with decreasing latitude (fig. 2). All models were improved by the inclusion of altitude as a fixed effect, with carbon fluxes showing a significant decrease with increasing altitude.

  ```{r echo=FALSE, out.width='100%', fig.cap = "Graph to show primary productivity $(MgCha^-1^yr^-1^)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("effect_of_latitude.png")
  ```

Latitude is a strong predictor for many of the carbon fluxes, explaining ~70% of variation in GPP (n = 241, p<0.01), 64% in NPP (n = 109, p<0.01) and 60% in ANPP (n = 252, p<0.01).

*Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?* All major carbon fluxes show similar responses to climate variables. Of the climate variables tested, annual wet days, aridity, cloud cover, mean diurnal temperature range and precipitation seasonality were poor explainers of variation in primary productivity, explaining less than 30% of the variation in each of the carbon fluxes.
We found that both measures of mean annual precipitation used were significant (p<0.05) but poor predictors of productivity, explaining at most 45% of variation in carbon flux. Despite being a poor predictor, the results indicate that there is a saturation point at between 3000 and 4000mm annual precipitation, above which productivity no longer increases.  
Looking across all productivity components, the climate variables which explain the highest amount of variation in carbon fluxes are temperature seasonality, mean annual temperature, annual temperature range, and vapour pressure. For measures of woody productivity (ANPP~woody~ and ANPP~woody stem~), potential evapotranspiration and vapour pressure deficit were also strong predictors.  
**Temperature seasonality**  
**Mean annual temperature**  
**Annual temperature range**  
**Vapour pressure**

*Do carbon fluxes vary in their responses to climate, particularly with regards to allocation between fluxes?*
